---
title: "Measuring My Time in Automotive Sales"
subtitle: "A short public data report"
author: "Hayk Manasyan"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
execute:
  warning: false
  message: false
---

# Executive Summary

---

# Context & Data

## Dataset Overview


## Key Fields

- Date
- New vs Used
- Make & Model
- Lead Source
- Follow-up activity (calls, texts, emails, videos)
- Trade-in indicator
- Front-end vs Back-end gross

## Data Notes

---

# Sales Cadence & Consistency

``` {r}
library(tidyverse)

sales <- read.csv("data/sales_data.csv")

start_date <- as.Date("2025-06-23")

sales_cadence <- sales %>%
  mutate(
    Date = as.Date(Date, format = "%m/%d/%Y"),
    prev_date = lag(Date, default = start_date),
    days_between = as.numeric(Date - prev_date)
  )

ggplot(sales_cadence, aes(x = days_between)) +
  geom_histogram(
    binwidth = 2,
    boundary = 0,
    fill = "steelblue",
    color = "white"
  ) +
  scale_x_continuous(
    breaks = seq(0, max(sales_cadence$days_between, na.rm = TRUE), by = 2)
  ) +
  scale_y_continuous(
    breaks = seq(0, 14, by = 2),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(
    title = "Days Between Consecutive Sales",
    subtitle = "Distribution of gaps between closed deals",
    x = "Days Between Sales",
    y = "Number of Deals"
  ) +
  theme_minimal()

```


``` {r}
mean(sales_cadence$days_between)
```

``` {r}
min(sales_cadence$days_between)

sales_cadence %>%
  summarise(
    same_day_sales = sum(days_between == 0, na.rm = TRUE)
  )
```

``` {r}
max(sales_cadence$days_between)

sales_cadence %>%
  filter(days_between == max(days_between)) %>%
  select(Date, prev_date, days_between)
```
---

# Product Mix & Specialization

---

# Effort Required to Close

---

# Lead Source Quality

---

# Deal Economics

---

# Key Takeaways

---

# Limitations & Notes

---

# Closing

